---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# selfbm

The goal of *selfbm* is to benchmark a function against itself by providing alternate
expressions in your code, separated by a `?` symbol.

It's very young and subject to changes, and only supports one use of `?` by function.

## Installation

``` r
# install.packages("remotes")
remotes::install_github("moodymudskipper/selfbm")
```

## Example

Define a function, and provide alternate statement for a call:

```{r example}
library(selfbm)
split_chars <- function(x){
  # some code
  # ...
  res <- c(substr(x,1,1), substr(x,2,2)) ? res <- strsplit(x,"")[[1]]
  # some more code
  # ...
  res
}
```

The function still works when called normally, using the left hand side call:

```{r cars}
split_chars("ab")
```

But when we use *selfbm* the call is parsed and alternatives are compared:

```{r}
selfbm(split_chars("ab"))
```

Several benchmarking packages are supported, *microbenchmark* (the default),
*bench*, and *rbenchmark*.

```{r}
selfbm(split_chars("ab"), engine = "bench")
selfbm(split_chars("ab"), engine = "rbenchmark", replications = 10000)
```
